---
title: "cooper's vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{cooper's vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(cooper)
```

This vignette shows you how to use 4 of the functions contained in the *cooper* library.

## 'myncurve()' for creating a Normal Dist. graph w/ q-value

If you have a normally distributed population, and you want to generate its graph and also calculate the lower-tail probability that a random specimen's result occurs at $\le$ to some measured 'q' value (that the curve represents the distribution for), then this is the function for you! You must give this function the 'q' result you're interested in, the 'mu' mean of the distribution, and the 'sigma' standard deviation of the distribution. Here's an example:

```{r}
myncurve(q = 6, mu = 10, sigma = 4)
```

Since 'q = 6' is one standard deviation smaller than the mean, then we expect that only the left (roughly) 16% of the area under the curve to be shaded in to indicate with the returned value that there's an approximately 16% chance of a specimen occurring with a measurement of 6 or lower.

## 'mynbin()' for calculating the Negative Binomial Probability at a point

If you have a binomial probability distribution, then you can use this function to calculate the probability of 'r' number of successes occurring given 'y' number of Bernoulli trials. Here's an example:

```{r}
mynbin(y = 6, r = 4, p = 0.8)
```

So if each Bernoulli trial has a p = 0.8 (which means 80%) chance of succeeding, the probability that r = 4 successes happen when running y = 6 trials is about 16%.

## 'myci()' for calc'ing a 95% Confidence Interval for the mean of a normally distributed, random sample

If you have a normally distributed, random sample, this function can calculate the 95% Confidence Interval for the mean of said sample. For example:

```{r}
myci(rnorm(25, mean = 10, sd = 5))
```

So the input is your data, but instead of bringing in some such data, I'll just create my own random, normally distributed data set via the 'rnorm()' function where it generates 25 random numbers from a normal distribution that  has a mean of 10 and standard deviation of 5. And then the result is an array of 2 numbers where the first number is the lower endpoint of the Confidence Interval and the second number is the upper endpoint of said interval.

## 'mycltu()' creates samples from a Uniform Distribution and then calc's the mean statistic and histograph

You give this function 4 inputs. 'n' is the size of every sample, 'iter' is the number of samples you want generated, and 'a' and 'b' are the lower and upper bounds (respectively) of the interval from which the code is allowed to randomly pick values, so it is effectively the domain of your Uniform Distribution. Here's an example:

```{r}
mycltu(30, 10000, 0, 10)
```

So this means we had the computer generate 10,000 samples, each with 30 specimens per sample. And we restricted the range of potential specimen values from 0 to 10. The resultant histograph also has 3 lines overlaid: a density curve made from the sample distribution, a theoretical normal curve, and the density from which the samples were taken.
